Determining Causes of Death with ChatGPT: A Case Study of Deaths from Verbal Autopsy in Sierra Leone from 2019-2022

### 2023-12-11 manuscript/manuscript.tex
Update manuscript

\title[Automatic Cause of Death Assignment from Verbal Autopsy Narratives with ChatGPT: A Case Study of Physician Agreed Deaths in Sierra Leone from 2019-2022]{Automatic Cause of Death Assignment from Verbal Autopsy Narratives with ChatGPT: A Case Study of Physician Agreed Deaths in Sierra Leone from 2019-2022}

>>>>

\title[Determining Causes of Death with ChatGPT: A Case Study of Deaths from Verbal Autopsy in Sierra Leone from 2019-2022]{Determining Causes of Death with ChatGPT: A Case Study of Deaths from Verbal Autopsy in Sierra Leone from 2019-2022}
